---
title: "The random parameters (or mixed) logit model 06102023"
author: "Constanza Avalos"
date: "2023-10-06"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## The random parameters (or mixed) logit model

This code follows the following tutorial: https://cran.r-project.org/web/packages/mlogit/vignettes/c5.mxl.html

We obtain the value of 26 euros for an hour of traveling, 5 euros for a change and 14 euros to travel in a more comfortable class. We then estimate a model with three random parameters, time, change and comfort. We first estimate the uncorrelated mixed logit model.

The presence of random coefficients and their correlation can be investigated using any of the three tests. Actually, three nested models can be considered, a model with no random effects, a model with random but uncorrelated effects and a model with random and correlated effects. We first present the three tests of no correlated random effects.

```{r data}
library("mlogit")
data("Train", package = "mlogit")
Train$choiceid <- 1:nrow(Train)
Tr <- dfidx(Train, choice = "choice", varying = 4:11, sep = "_",
            opposite = c("price", "comfort", "time", "change"),
            idx = list(c("choiceid", "id")), idnames = c("chid", "alt"))
Tr
Tr$price <- Tr$price / 100 * 2.20371
Tr$time <- Tr$time / 60
Train.ml <- mlogit(choice ~ price + time + change + comfort | - 1, Tr)
coef(summary(Train.ml))

coef(Train.ml)[- 1] / coef(Train.ml)[1] #we get monetary values

Train.mxlu <- mlogit(choice ~ price + time + change + comfort | - 1, Tr,
panel = TRUE, rpar = c(time = "n", change = "n", comfort = "n"), R = 100,
correlation = FALSE, halton = NA, method = "bhhh")
names(coef(Train.mxlu))

Train.mxlc <- update(Train.mxlu, correlation = TRUE)
names(coef(Train.mxlc))

marg.ut.time <- rpar(Train.mxlc, "time")
summary(marg.ut.time)

wtp.time <- rpar(Train.mxlc, "time", norm = "price")
summary(wtp.time)

#another example

data("RiskyTransport", package = "mlogit")
RT <- dfidx(RiskyTransport, choice = "choice", idx = list(c("chid", "id"), "mode"),
            idnames = c("chid", "alt"))
ml.rt <- mlogit(choice ~ cost + risk  + seats + noise + crowdness + convloc + clientele | 0, data = RT, weights = weight)
summary(ml.rt)

mx.rt <- mlogit(choice ~ cost + risk  + seats + noise + crowdness + convloc + clientele | 0, data = RT, weights = weight,
rpar = c(cost = 'zbt', risk = 'zbt'), R = 100, halton = NA, panel = TRUE)
summary(mx.rt)

indpar <- fitted(mx.rt, type = "parameters")
head(indpar)

indpar$VSL <- with(indpar, risk / cost * 100)
quantile(indpar$VSL, c(0.025, 0.975))
mean(indpar$VSL)
max(indpar$cost)
max(indpar$VSL)

```

## Including Plots

You can also embed plots, for example:

```{r results='asis', echo=FALSE}

library(texreg)
htmlreg(list('Multinomial logit' = ml.rt, 'Mixed logit' = mx.rt),digits = 3, float.pos = "hbt", label = "tab:risktr", single.row = TRUE, caption = "Transportation choices.")

library("ggplot2")
RT$id <- RT$id
indpar <- merge(unique(subset(as.data.frame(RT),
                              select = c("id", "african"))),
                indpar)
ggplot(indpar) + geom_density(aes(x = VSL, linetype = african)) + 
    scale_x_continuous(limits = c(200, 1200))

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
